---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)
```

# formantdistsim

<!-- badges: start -->
<!-- badges: end -->

```{r setup}
library(formantdistsim)
library(tidyverse)
```

This package is supposed to simulate an underlying binomial, or logistic change, where the data is generated from a different gaussian, depending on which category was chosen.

-   `phi`: the weight on the beta distribution. Higher = more closely clustered together probabilities.

-   `n`:The number of samples from each "speaker"

-   `pop_size`: the number of "speakers"

-   `mu1`/`mu2`: the $\mu$ of each distribution

-   `sigma1`/`sigma2`: the $\sigma$ of each distribution

-   `logit_low`/`logit_high` the start and end point, in logit space, of the probabilistic change.

```{r}
set.seed(200)

sim_prob_cont(
  max_year = 100,
  phi = 10, 
  n =  50, 
  pop_size = 100, 
)->
  simulated
```

```{r}
#| label: simulated data
simulated |>
  group_by(id) |> 
  summarise(
    value = mean(value),
    dob = mean(dob)
  ) |> 
  ggplot(aes(dob, value))+
    geom_point()
```
